Data Quality - Data Analysis

### 2025-07-01 study2sona/analysis/analysis.qmd
bits and bobs
lesgoo

df <- read.csv("../../study2/data/rawdata_participants.csv") |> 
  mutate(Condition = fct_relevel(Condition, "Prolific", "Attention Checks", "Quiz", "Control"))
```

```{r}

```

@@

```{r}
m1 <- glm(Failed ~ Prolific, 
          data=mutate(df, Prolific = ifelse(Condition == "Prolific", "Prolific", "SONA")), 
          family="binomial")
# m1 <- brms::brm(Failed ~ Condition, data=df, family="poisson", backend="cmdstanr")

@@

modelbased::estimate_means(m1, by="Condition") |> 
  plot()
```

>>>>

df <- read.csv("../../study2/data/rawdata_participants.csv") |> 
  mutate(Prolific = ifelse(Condition == "Prolific", "Prolific", "SONA"))
```

## Enjoyment

```{r}
df |> 
  summarise(n = n(), .by=c("Prolific", "Experiment_Enjoyment")) |>
  filter(!is.na(Experiment_Enjoyment)) |> 
  mutate(n = n / sum(n),
         Experiment_Enjoyment = fct_rev(as.factor(Experiment_Enjoyment)),
         .by="Prolific") |>
  ggplot(aes(y = Prolific, x = n, fill = Experiment_Enjoyment)) +
  geom_bar(stat="identity", position="stack") +
  scale_fill_manual(values=c("green", "yellowgreen",  "yellow", "orange", "red")) +
  scale_x_continuous(expand=c(0, 0))  +
  labs(title="Experiment Enjoyment",
       subtitle="Proportion of participants by condition") + 
  guides(fill = guide_legend(reverse=TRUE)) +
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "top",
        legend.title = element_blank())

lm(Experiment_Enjoyment ~ Prolific, data = df) |> 
  modelbased::estimate_contrasts(p_adjust="none", contrast = "Prolific") |> 
  display()

m1 <- lm(Experiment_Enjoyment ~ Prolific, data=df)

summary(m1)
```

@@

```{r}
m1 <- glm(Failed ~ Prolific, 
          data=df, 
          family="binomial")
# m1 <- brms::brm(Failed ~ Condition, data=df, family="poisson", backend="cmdstanr")

@@

modelbased::estimate_contrasts(m1)
modelbased::estimate_means(m1, by="Condition") |> 
  plot()
```
